The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Add cohesive network slide

# How does the tool identify what a ‘cohesive network’ might look like?

>>>>

### How to identify a ‘cohesive network’?

- 'Long term layer'
- Intended to show what a joined-up cycle network could look like if we were to consider new cycleways by either closing roads to motorised traffic or creating one-way systems
- Find  roads that have high cycling potential on some or all of their length
- Join them up!

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-cohesive-leeds.png)
